Collapse Weddell and Check consistency

### 2023-08-23 WeddellSea_collapse.Rmd
Change name of Rmd

---
title: "Check consistency"
author: "L.A.S."
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

calc_topological_indices(gM)
write_csv(collapsed_w,"Data/Weddell_collapsed_links.csv")
```

>>>>

---
title: "Collapse Weddell and Check consistency"
author: "L.A.S."
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

calc_topological_indices(gM)
write_csv(collapsed_w,"Data/Weddell_collapsed_links.csv")

collapsed_w <- read_csv("Data/Weddell_collapsed_links.csv")

# Weddell Sea get full classification

```{r, WeddellSeaFullClass, eval=F,echo=F,message=T,warning=T}

# Check valid names 
#
# Predators
require(taxize)
dfn <- unique(dtot$consumer)
dfn <- c(dfn, unique(dtot$resource))
dfn <- unique(dfn)

# CLasificación completa

clasall <- classification(dfn, db = 'gbif') #

class_list <- class_to_df(clasall)

classall_df <- class_list[[1]]

#
# Search in worms records Not found in gbif
#

dfn <- class_list[[2]]$Taxon

clasall <- classification(dfn, db = 'worms') #

class_list <- class_to_df(clasall)

tmp_df <- class_list[[1]]
names(tmp_df) <- tolower(names(tmp_df))
names(tmp_df)[1] <- "Taxon"
dfn <- class_list[[2]]$Taxon
names(classall_df)
classall_df <- bind_rows(classall_df,tmp_df)
saveRDS(classall_df,file="Data/WeddellSea_clasification.rds")

search_value <- "foram"
result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))

search_value <- "Hexactinellida"
result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))

search_value <- "Bacillariophyceae"
result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))

dtot1 <- replace_nodes(dtot, result, "class")
collapsed_w <- dtot1 %>% distinct()
gM <- graph_from_edgelist(as.matrix(collapsed_w), directed  = T)

degree(gM)["Bacillariophyceae"]
degree(gM)["Pleuragramma antarcticum"]
require(NetIndices)
a <- get.adjacency(gM,sparse=F)
tl <- TrophInd(a)
tl[rownames(tl)=="Pleuragramma antarcticum",]
tl[rownames(tl)=="Pygoscelis adeliae",]
trophiclevels(gM)
search_value <- "Chromista"
result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))

search_value <- "Dictyocha"
result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))
```
